---
title: "Dota2_Data_Mining"
output:
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r chunk}
df <-read.csv("dota2.csv")
```




## 1----------------------------------------------------------------------------

## Summary of Duration (Quantative Variable)

## Mean
```{r}

mean(df$duration,trim = 0, na.rm = FALSE)

cat("\nStandard Deviation: ")
sd(df$duration)

cat("\nFive number summary: \n")
summary(df$duration)
```


## Histogram of Duration 
```{r}

hist(df$duration,
     main = "Dota2 game Length (Positive Skewed Distribution)",
     xlab = "Game duration (sec)",
     col = "pink",
     probability = TRUE)
#
lines(density(df$duration),col = "blue")

```

## Quantile-Quantile Plots qqplots
```{r}
qqnorm(df$duration,
       main = "QQPlot (Positive Skewed Distribution)",
       ylab = "Duration (sec)")
qqline(df$duration)
```
## Box Plot
```{r}

boxplot(df$duration,
        main ="BoxPlot (Positive Skewed Distribution) ",
        horizontal = TRUE,
        xlab = "Duration (sec)")

```
## Outliers
```{r}

IQR(df$duration, na.rm = FALSE)
out <- boxplot.stats(df$duration)$out
out_ind <- which(df$duration %in% c(out))
out_ind
df[out_ind,]

```
## 2----------------------------------------------------------------------------

## Graphical Display of multiple variables and their correlation

```{r}
plot(df$duration,df$first_blood_time,
     main = "Multiple variable Graphical Display",
     xlab = "Duration (sec)",
     ylab ="First blood Time (sec)",
     col = "blue",
     pch = 19)


print("Correlation: From the scatter plot we can assume that the First Blood time is densely populated around 2000s - 3000s(mid game) in duration. So, we can say that around mid game there is higher chance of getting first blood than during early and late game. ")

```
## 3----------------------------------------------------------------------------

## Frequency Table
```{r}


cat("Frequency Table\n")
cat("\n")
table(df$radiant_win)

```

## Relative Frequency Table
```{r}

cat("Relative Frequency Table\n")
cat("\n")
table(df$radiant_win)/length(df$radiant_win)

cat("\n")
cat("47.2% of all values in the data set are FALSE.\n")
cat("52.8% of all values in the data set are TRUE.\n")
```

## 4----------------------------------------------------------------------------

## Two way table 
```{r}

#create data frame
data_F <- data.frame(df$ability_name,df$radiant_win)

#view data frame
data_F

#create two way table from data frame
two_way_table <- table(df$ability_name,df$radiant_win)

#display two way table
two_way_table


cat("\n")
cat('\nRelationship between two Variables:\n')
cat('\nThe game revolves around the Heroes, their ability, items and their play style or skills of the players and many other independent variables. But the relationship between ability_name and radiant_win is also strong in this case. There are many games in which any ability_name can wipe out opponent team which can cause the radiant_win to be TRUE in this case.
')


```

## 5----------------------------------------------------------------------------

## Side by side plot for one categorical and quantative varible.


```{r}



par(mfrow=c(1,2))
plot(df$duration,
     main="Scatterplot of Duration (sec)",
     xlab = "",
     ylab = "Duration")

plot(df$item_id,
     main="Scatterplot of Item Id",
     xlab = "",
     ylab = "Item ID")

cat("")


cat("Duration Summary: \n")
summary(df$duration)

cat("\nItem Id Summary: \n")
summary(df$item_id)

```
## 6----------------------------------------------------------------------------

#Visualization of Data
```{r}

barplot(df$item_id,
        main = "Bar Chart",
        xlab = "Item Id")

scatter.smooth(df$item_id,
               main = "Scatter Plot")


require(ggplot2)
data <- read.csv("dota2.csv", header = TRUE)
data <- data.matrix(data[,-1])
heatmap(t(data),
        main = "Heat Map",
        Rowv = NA,
        Colv = NA,
        col = heat.colors(200,alpha = 1,rev = FALSE),
        scale = "row")




cat("Summary statistics: \n")
summary(df$item_id)           


```



Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
it